Recursive formula:
$ C_0 = C_1 = 1 $

$ C_n = \sum_{k = 0}^{n-1} C_k C_{n-1-k} , {n} \geq 2 $

Analytical formula:
$ C_n = \binom{2n}{n} - \binom{2n}{n-1} = \frac{1}{n + 1} \binom{2n}{n} , {n} \geq 0 $

The first few numbers Catalan numbers, $C_n$ (starting from zero): $1, 1, 2, 5, 14, 42, 132, 429, 1430, \ldots$

The Catalan number $C_n$ is the solution for:
\begin{itemize}

  \item Number of correct bracket sequence consisting of $n$ opening and $n$ closing brackets.
  \item The number of rooted full binary trees with $n + 1$ leaves (vertices are not numbered). A rooted binary tree is full if every vertex has either two children or no children.
  \item The number of ways to completely parenthesize $n + 1$ factors.
  \item The number of triangulations of a convex polygon with $n + 2$ sides (i.e. the number of partitions of polygon into disjoint triangles by using the diagonals).
  \item The number of ways to connect the $2n$ points on a circle to form $n$ disjoint chords.
  \item The number of non-isomorphic full binary trees with $n$ internal nodes (i.e. nodes having at least one son).
  \item The number of monotonic lattice paths from point $(0, 0)$ to point $(n, n)$ in a square lattice of size $n \times n$, which do not pass above the main diagonal (i.e. connecting $(0, 0)$ to $(n, n)$).
  \item Number of permutations of length $n$ that can be stack sorted (i.e. it can be shown that the rearrangement is stack sorted if and only if there is no such index $i < j < k$, such that $a_k < a_i < a_j$ ).
  \item The number of non-crossing partitions of a set of $n$ elements.
  \item The number of ways to cover the ladder $1 \ldots n$ using $n$ rectangles (The ladder consists of $n$ columns, where $i^{th}$ column has a height $i$).
  
\end{itemize}